A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-20 papers/execution-model/model.tex
Add files via upload
updated bio.bib

Smart contracts rarely live in isolation. To reach their full
potential, it should be possible to integrate them with traditional
software systems and to enable input from outside the blockchain. Such
input requires trusted intermediaries that run so-called oracles \cite{oracles}. A
smart contract registers a request and a callback with an oracle. The
oracle invokes the callback as soon as an answer is available.

@@

The execution model is an abstraction of the Tezos blockchain \cite{Tezos}
augmented with functional (OCaml) programs that interact with the
blockchain. As the blockchain is realized by a peer-to-peer network of
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes that execute in a
safe-safe way. Tezos' smart contract language Michelson and its
properties have been formalized elsewhere \cite{type-safe-michelson}.

@@

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of smart contracts. Oracles \cite{oracle-patterns}\cite{call-action-oracle}\cite{oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network. A blockchain oracle is used to provide external data to smart contracts. Several researches have been done to provide oracle solutions for blockchain. The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles. This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications. Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain. For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum. The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$. 
For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.

>>>>

Smart contracts rarely live in isolation. To reach their full
potential, it should be possible to integrate them with traditional
software systems and to enable input from outside the blockchain. Such
input requires trusted intermediaries that run so-called oracles \cite{oracle-patterns, call-action-oracle}. A
smart contract registers a request and a callback with an oracle. The
oracle invokes the callback as soon as an answer is available.

@@

The execution model is an abstraction of the Tezos blockchain \cite{tezos-whitepaper}
augmented with functional (OCaml) programs that interact with the
blockchain. As the blockchain is realized by a peer-to-peer network of
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes that execute in a
safe-safe way. Tezos' smart contract language Michelson and its
properties have been formalized elsewhere \cite{type-safe-michelson}.

@@

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of smart contracts. Oracles \cite{oracle-patterns, call-action-oracle, oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network. A blockchain oracle is used to provide external data to smart contracts. Several researches have been done to provide oracle solutions for blockchain. The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles. This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications. Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain. For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum. The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$. 
For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.
